Face Attractiveness and the Sense of Reality

### 2022-08-25 analysis.Rmd
update

df <- read.csv("data/data.csv") 
# |>
#   mutate(
#     Date = lubridate::dmy(Date),
#     Participant = fct_reorder(Participant, Date),
#     Screen_Refresh = as.character(Screen_Refresh),
#     Illusion_Side = as.factor(Illusion_Side),
#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
#     Block = as.factor(Block),
#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
#   )

@@

```{r message=FALSE, warning=FALSE}
dfsub$Cor_Trustworthy <- NA
dfsub$Cor_Attractive <- NA
for(participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
}
```

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
  rbind(dfsub) |> 
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```

@@

```{r message=FALSE, warning=FALSE}
df |> 
  ggplot(aes(x = Real, y = Participant, fill=Participant)) +
  ggdist::stat_slab(scale=2, slab_alpha = 0.9) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(limits = c(-100, 100), 
                     expand = c(0.01, 0.01),
                     breaks = c(-100, 0, 100),
                     label = c("Fake", "0", "Real")) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title= "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5))
```

### Simulation Monitoring

>>>>

df <- read.csv("data/data.csv")
# |>
#   mutate(
#     Date = lubridate::dmy(Date),
#     Participant = fct_reorder(Participant, Date),
#     Screen_Refresh = as.character(Screen_Refresh),
#     Illusion_Side = as.factor(Illusion_Side),
#     # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
#     Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
#     Block = as.factor(Block),
#     Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
#   )
```

@@

```{r message=FALSE, warning=FALSE}
dfsub$Cor_Trustworthy <- NA
dfsub$Cor_Attractive <- NA
for (participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
}
```

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm = TRUE))) |>
  rbind(dfsub) |>
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |>
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```

```{r message=FALSE, warning=FALSE}
df |>
  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
    summarize(Real = mean(Real)) |>
    ungroup() |>
    arrange(Real) |>
    pull(Participant))) |>
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(-100, 100),
    expand = c(0.01, 0.01),
    breaks = c(-100, 0, 100),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

### Reality and Attractiveness

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Real ~ Attractive + (1|Participant), data = df)
```

```{r message=FALSE, warning=FALSE}
pred <- estimate_relation(model, at = c("Attractive"))

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  geom_point() +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted))
```
